A Detection of the Environmental Dependence of the Stellar Profiles and haloes of Massive Central Galaxies

### 2017-07-14 draft/paper2.tex
Need new discussion

        \item a 10 kpc radii (hereafter noted \minn{}) as proxy of the ``in situ'' 
            stellar component. 
            This is motivated by recent observations and simulations 
            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}).

@@

    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
    the \mtot{}-matched samples suggests that environment does not play a major role 
    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
    similar \mstar{} in the \textit{in situ} component}, how does environment affect 
    their subsequent mass assembly?
    Assuming \minn{} is reasonable tracer of the ``in situ'' mass, we compare the 
    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
    massive central galaxies in more massive haloes host much more prominent outer 
    stellar halo.

@@

@@

    \song{Keep the relevant session from previous draft, need some works.}
    By using deep imaging from the HSC survey we have shown that the stellar mass 
    density profiles of massive central galaxies depend systematically on the mass 
    of their host dark matter haloes. 
    Here we discuss the physical origin, scientific implications, and potential 
    caveats of this result.

\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
            Build-Up of Outer Envelopes}

    Our results are consistent with the picture that massive central galaxies form via 
    a ``two-phase'' scenario. 
    According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
    during an intense period of in situ star formation. 
    The outskirts of massive galaxies are then built up via a more gradual second 
    phase of evolution (the ``ex-situ'' phase) which is dominated by mass growth via 
    the accretion of satellite systems. 
    Non-dissipative minor mergers mostly deposit stars on the outskirts of the 
    centrals and do not have large impact on the central \mden{} profile 
    (e.g. \citealt{Oogi2013, Bedorf2013}). 
    Hence, according to this picture, the outer stellar envelopes of massive centrals 
    should correlate with the masses of their host haloes, in qualitative agreement with
    our findings.

@@

    We now investigate to what degree our assumption that the inner 10 kpc \mstar{}
    corresponds to an in situ mass.    
    Fig \ref{fig:discussion_1} compares the median \mden{} profiles of the 
    galaxies in two \mtot{} bins 
    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with 
    (1) the median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
    \citealt{Patel2013} since they are considered as the progenitors of 
    ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$.    
    (2) the inner components of $z{\sim} 0$ ellipticals from 2-D decomposition 
    (\citealt{Huang2013a}).
    As proxy of the in situ components, \citet{Huang2013b} showed they are 
    structurally similar to the compact ``red nuggets'' at high-$z$. 
    (3) the ``in situ'' components of simulated central galaxies in massive haloes 
    from \citet{Cooper13} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
    resolution).  
    The comparison confirms that \minn{} should be reasonable proxy of the 
    ``in situ'' mass\footnote{We convert these \mden{} profiles to the same 
    Chabrier IMF; but there are still differences in median \mstar{} and 
    details in the \m2l{} estimates}.  
    More importantly, it shows that the \mden{} profile at 
    $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
    to the ``in situ'' processes.

    We also compare with a uniquely massive BCG at high redshift: 
    a ${\sim} 10^{11.4} M_{\odot}$ BCG with distinctive ``cD''-like envelope at 
    $z{\sim} 1.1$ (\citealt{Liu2013}).  
    Its \mden{} profile follows the median profile of $11.6\leq$\logmtot{}$<11.8$ 
    massive galaxies nicely inside 10-15 kpc, but becomes much steeper in the outskirt.  
    This unique object may present an interesting case where the inner ``core'' of a 
    massive BCGs is already in pace at $z{\sim} 1$ when its extended envelope is still
    under construction.
    More BCGs like this at $0.5 < z < 1.0$ can shed light on this intriguing 
    process, and help us confirm whether the environmental dependence of structure 
    has already emerged within massive galaxies at higher redshift 
    (e.g. \citealt{Papovich2012})
%% ------------------------------------------------------------------------------------ %%

@@

\subsection{Scatter in Outer Stellar Enveloppes and ``cD'' Galaxies}

   The thin lines in Figure \ref{fig:prof_1} show the \mden{} density profiles of 
   individual galaxies. 
   In general, we find that any given galaxy has a relatively smooth profile, even out 
   to large radii, however, on a galax-by-galaxy basis there is a large (but continuous) 
   variation in the amplitude of \mden{} at large scales. 
   Traditionally, the so-called ``cD'' galaxies are defined to have large stellar 
   envelopes and are found at the hearts of massive clusters (\citealt{Matthews1964, 
   Schombert1988}). 
   However, until present, it has not been clear whether ``cD'' galaxies are a distinct 
   and special population, or if they are simply the continum of a smoothly varying 
   population. 
   Fig \ref{fig:prof_1} shows that with the help of our deep HSC images, we can directly 
   map out the variations in \mden{} profiles at large scales. 
   Instead of a bi-model distribution, we find that the outskirts of massive galaxies 
   display a smooth but continuous variation. 
   We can hence conclude that ``cD'' galaxies are simply the extremes of a continuous 
   population but that do not necessarily form a unique a special class of galaxies. 
   This suggests that it might not be very physically meaningful to separate these 
   massive galaxies into two arbitrary morphological classes (``cD'' versus non-``cD''). 
   This conclusion is similar to those of \citep{Zhao2015} who found that a large 
   fraction of nearby BCGs (34\%) does not fall into the ``cD'' class. 
   Our finding that massive galaxies display a diverse range of outer stellar 
   envelope is also supported by HST observations of BCGs at $0.3 < z <0.9$ 
   by \citealt{Bai2014}.

@@

%\acknowledgements
\section*{Acknowledgements}

@@

%%%%%%%%%%: Bibliographic Section %%%%%%%%%%

\bibliographystyle{mnras}
\bibliography{redbcg}

>>>>

        \item a 10 kpc radii (hereafter noted \minn{}) as proxy of the 
            \textit{in situ} stellar component. 
            This is motivated by recent observations and simulations 
            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}).

@@

    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
    the \mtot{}-matched samples suggests that environment does not play a major role 
    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
    similar \mstar{} in the \textit{in situ} component}, how does environment affect 
    their subsequent mass assembly?
    Assuming \minn{} is reasonable tracer of the \textit{in situ} mass, we compare the 
    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
    massive central galaxies in more massive haloes host much more prominent outer 
    stellar halo.

@@

%% ------------------------------------------------------------------------------------ %% 
%% Discussion 
%% ------------------------------------------------------------------------------------ %%

@@

    Using the deep images from the HSC survey, we show that the stellar mass 
    distributions of massive central galaxies at $0.3 < z < 0.5$ depend on their 
    environment or \mhalo{}. 
    Here we briefly discuss the physical implications and potential caveats of this 
    result.

%% ------------------------------------------------------------------------------------ %% 
\subsection{The Role of Environment in the ``Two--Phase'' Formation of 
            Massive Central Galaxies}

    Results presented here are broadly consistent with the picture that massive central 
    galaxies form via a ``two-phase'' picture.

    According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
    during an intense period of \textit{in situ} star formation. 
    The outskirts of massive galaxies are then built up via a more gradual second 
    phase of evolution (the ``ex-situ'' phase) which is dominated by mass growth via 
    the accretion of satellite systems. 
    Non-dissipative minor mergers mostly deposit stars on the outskirts of the 
    centrals and do not have large impact on the central \mden{} profile 
    (e.g. \citealt{Oogi2013, Bedorf2013}). 
    Hence, according to this picture, the outer stellar envelopes of massive centrals 
    should correlate with the masses of their host haloes, in qualitative agreement with
    our findings.

@@

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{Scatter in Outer Stellar Enveloppes and ``cD'' Galaxies}

   The thin lines in Figure \ref{fig:prof_1} show the \mden{} density profiles of 
   individual galaxies. 
   In general, we find that any given galaxy has a relatively smooth profile, even out 
   to large radii, however, on a galax-by-galaxy basis there is a large (but continuous) 
   variation in the amplitude of \mden{} at large scales. 
   Traditionally, the so-called ``cD'' galaxies are defined to have large stellar 
   envelopes and are found at the hearts of massive clusters (\citealt{Matthews1964, 
   Schombert1988}). 
   However, until present, it has not been clear whether ``cD'' galaxies are a distinct 
   and special population, or if they are simply the conti of a smoothly varying 
   population. 
   Fig \ref{fig:prof_1} shows that with the help of our deep HSC images, we can directly 
   map out the variations in \mden{} profiles at large scales. 
   Instead of a bi-model distribution, we find that the outskirts of massive galaxies 
   display a smooth but continuous variation. 
   We can hence conclude that ``cD'' galaxies are simply the extremes of a continuous 
   population but that do not necessarily form a unique a special class of galaxies. 
   This suggests that it might not be very physically meaningful to separate these 
   massive galaxies into two arbitrary morphological classes (``cD'' versus non-``cD''). 
   This conclusion is similar to those of \citep{Zhao2015} who found that a large 
   fraction of nearby BCGs (34\%) does not fall into the ``cD'' class. 
   Our finding that massive galaxies display a diverse range of outer stellar 
   envelope is also supported by HST observations of BCGs at $0.3 < z <0.9$ 
   by \citealt{Bai2014}. 
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Summary 
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
%% Acknowledgements 
%% ------------------------------------------------------------------------------------ %% 
\section*{Acknowledgements}

@@

%% ------------------------------------------------------------------------------------ %% 
%% References  
%% ------------------------------------------------------------------------------------ %% 
\bibliographystyle{mnras}
\bibliography{redbcg}
